Chemically Self-Consistant Modeling of the Globular Cluster NGC 2808 and its Effects on the Inferred Helium abundance of Multiple Stellar Populations.

### 2024-03-24 refResponse/response.txt

# Response to the referee for the paper titled
# Chemically Self-Consistant Modeling of the Globular Cluster NGC 2808 and its Effects on the Inferred Helium abundance of Multiple Stellar Population.

We thank the referee for their careful reading and critique of our work. Below
we have attached a response to the referees comments enumerated in the same
manner in which we recived the report. All changes to the text of the manuscript
have been placed in boldface.

# Comment 1 [Chromosome Maps] [TODO [ x ]]
Referee:
  Milone et al. 2015 and other groups identified five distinct populations in NGC
  2808. To do so they used the chromosome map, a color-color combination of
  filters (including F814W and F275W, the two filters used in this study). This
  diagnostic tool was introduced to maximize the separation between stars with
  different light-element abundances (different filters are in fact sensitive to
  different light-elements), information which, as demonstrated, can only be
  partially retrieved from a (F275W-F814W, F814W) CMD. The authors do not justify
  the choice to use the (F275W-F814W, F814W) CMD, instead of the chromosome map.
  Furthermore, although the authors only find two populations from their
  analysis, they do not comment on why this is the case and, importantly, how
  this compares with what Milone et al. 2015 and others found. Finally, it is
  neither clear nor physically motivated why the method used in their work should
  be a better method for identifying multiple populations than the chromosome
  map. This is a crucial point and is completely missing.
Response:
  Overall, in response to this point, we have added text to the paper to
  summarize why we elect to not make use of chromosome maps. The summary of
  that additional text is that we do not belive we have an appropriate emough
  handle on the uncertanties in the chromosome maps to allow us to make
  statistically signifigant statements about population seperation. Due to the
  manner in which chromosome maps are constructed the fractional uncertanties
  of datapoints grow rapidly when compared to what they would be in on either a
  color-magnitude diagram or color-color diagram. We investigate this and found
  that the best-case (assuming no error on the red and blue fiducial line
  positioning and only possion error on each magnitude measurment) mean
  fractional error after computing a chromosome map was > 1. (See
  https://algebrist.com/~tboudreaux/files/ChromosomeMapFractionalErrorDist.pdf
  for the probability density distribution of fractional errors over the
  chromosome map parameter space). Because Fidanka fundamentally finds clusters
  based on a mean density derived from a monte carlo sampling of the error
  space, such large uncertanties prevent fidanka from identifying clusters
  reliably. CMD space does not face the same issues. It is true that we may be
  sacrificing some of the light-element abundance-variation driven seperation
  between potential stellar populations; however, as the aim of this work is to
  identify if chemically-self consistent modeling has a signifigant affect on
  the infered helium abundance it is not strictly nessisary to extract all
  previously identified populations. Finally, as there has been recent
  literature which questions whether there are in fact more than 2 populations
  in NGC 2808 (Valle et al. 2022, based on spectroscopy) we feel that it would
  be improper to not take an extremley careful handleing of clustering and
  the uncertanties which play into it.

# Comment 2 [Chemical Self-Consistency] [TODO [ x ]]
Referee:
  Although the authors state several times that the work adopts a chemically
  self-consistent modeling of the globular cluster, it is not explained what
  the improvement is in this work compared to previous ones. Furthermore, it is
  not clear what the chemical composition of the two populations is (in terms
  of [Fe/H], [O/Fe], [N/Fe] etc.) and what the motivation behind this choice
  is. The authors refer to Milone et al. 2015 again but without further
  explanation and it is not up to the reader to go and read that paper. The
  paper must be comprehensive and all important information used must be
  clearly mentioned and reported. Finally, that paper provides the chemical
  content of the other three multiple populations (B, C and D). Why do the
  authors specifically use the chemical content of population E? The
  motivations for this are unclear, but very important.
Response:
  By chemically self-consistent we mean that unlike the majority of globular
  cluster modeling efforts we use high temperature opacities, low temperature
  opacities, atmosphereic bounday conditions, and structural compositons which
  all agree in their atmoic mass fractions up to Zinc (with heavier elements
  being excluded as the OPLIB high-temperature opacity tables we use have not
  been computed above zinc). This has been done, to the best of our knowledge,
  for only one other cluster, NGC 6752 (Dotter et al. 2015). That work showed
  that full chemical self-consistancy did not result in a signifigant change to
  the infered helium abundances. Here we are essentially reproducing this work
  but for another cluster which has a more extreme infered helium abundance in
  the literature thus showing that the NGC 6752's lack of response to self
  consistent models is not unique to that cluster and may be expected to be a
  more general feature of the Galactic globular cluster population. We have
  added text to this effect in the abstract of the manuscript. We also include
  text in the paper to explain why we use populations A and in E in specific.
  These two populations have the lowest and highest infered helium abundances
  respectivley and have been consitantly shown to be seperable in the NGC 2808
  CMD. As we are focusing on determining if chemically self-consistent modeling
  will affect the infered helium abundance it makes sense to use the most
  extreme models. Finally, we have included a table of abundance ratios for the
  two populations which we use in the text of the manuscript.

# Comment 3 [Initial Guesses] [TODO [ ]]
Referee:
  Similar to the previous comment, the authors do not mention the literature
  values adopted as first guess for the cluster age, distance and reddening.
  They do not comment on whether there is agreement between these values and
  the best-fit parameters. This, in my opinion, is fundamental to understand
  whether the best-fit solution obtained is reliable or not.
Response:
  Text has been added to the manuscript stating what the initial guesses were
  and how these values compare to the best fit parameters. The summary of this
  is that the best fit parameters are multiple sigma removed from the initial
  guess.

# Comment 4 [Mixing Length Parameter] [TODO [ ]]
Referee:
  The best-fitting isochrones for Populations A and E in Table 1 have very
  different mixing length parameters (2.050 vs 1.600). This difference has a
  significant impact on the effective temperature (especially on the red giant
  branch) and is not physically justified in the text. In fact, there is no
  obvious reason to believe that two populations in the same cluster could have
  such different mixing lengths. However, this has a huge effect on the results
  obtained. Why didn't the authors set this parameter to be the same in both
  isochrones? What would have been the results in this case?
Response:
  The mixing length traces the adiabicity of the upper atmosphere of a star,
  encoding a complex, turbulent, 3D phenomenon. This adiabicity and the
  turbulence should be strongly coupled to the mean molecular mass. The two
  populations, A and E, have very different mean molecular masses due to the
  dramatically enhanced helium abundance in population E. It is therefore not
  suprising or at least not alarming that the mixing lengths are not in
  agreement. We have added text to the manuscript clarifing that this
  difference in best fit mixing lengths is not alarming.

# Comment 5 [Figure Clarity] [TODO [ ]]
Referee:
  Some of the Figures they present are not easily readable and understandable,
  of which Figure 6 is an example. It is not clear how to read the
  uncertainties on the different parameters from this figure (which are not
  even reported in Table 1). Furthermore, it is not explained in the text why
  the authors use the ACS artificial star tests to derive these uncertainties,
  when they could use the same Monte Carlo approach to make robust uncertainty
  predictions for each of the parameters.
Response:
  TBD

# Comment 6 [Copy Editing] [TODO [ ]]
Referee:
  While reading the paper I noticed several typos, truncated sentences and few
  unanswered questions. The authors should read through the paper and clean up
  these issues.
Response:
  We have gone through the manuscript and further copy-edited it.

### 2024-03-24 src/sections/fitting.tex
Fixed broken figure labels
Started incorporating ref suggestions into text of the paper

\begin{figure*}
  \centering
  \includegraphics[width=0.9\textwidth]{src/figures/BestFitResults.pdf}
  \label{fig:BestFitResults}
  \caption{Best fit isochrone results for NGC 2808. The best fit population A
  and E models are shown as black lines. The following 50 best fit models are
  presented as grey lines. The solid black line is fit to population A, while
  the dashed black line is fit to population E.}
\end{figure*}

\begin{table*}
  \centering
  \begin{tabular}{c | c c c c c c}
    \hline
    Population & Age & Distance Modulus & Extinction & Y & $\alpha_{ML}$ & $\chi^{2}_{\nu}$\\
    & [Gyr] & & [mag] & & &\\
    \hline
    \hline
    A & 12.996$^{+0.87}_{-0.64}$ & 15.021 & 0.54 & 0.24 & 2.050 & 0.021\\
    E & 13.061$^{+0.86}_{-0.69}$ & 15.007 & 0.537 & 0.39 & 1.600 & 0.033 \\
    \hline
  \end{tabular}
  \label{tab:BestFitResults}
  \caption{Best fit parameters derived from fitting isochrones to the fiducual lines derived from the NCG 2808 photometry. The one sigma uncertainty reported on population age were determined from the 16th and 84th percentiles of the distribution of best fit isochrones ages.}
\end{table*}

@@

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.90\textwidth]{src/figures/photometricOffset.pdf}
  \label{fig:offset}
  \caption{(left) CMD showing the photometric offset between the ACS and HUGS data for NGC 2808. CMDs have been randomly subsampled and colored by point density for clarity. (right) Mean difference between the color of the HUGS and ACS fiducual lines at the same magnitude. Note that the ACS data is systematically bluer than the HUGS data.}
\end{figure*}

The oberved photometric offset between ACS and HUGS reductions introduces a
systematic uncertainity when comparing parameters derived from isochrone fits
to ACS data vs those fit to HUGS data. Specifically, this offset introduces a
{\color{red}$\sim$AGE Gyr} uncertainity. Moreover, for two isochrone of the
same age, only seperated by helium mass fraction, a shift of the main sequence
turn off of is also expected. Figure \ref{fig:HeMO} shows this shift. Note a change in the helium mass fraction of a model by 0.03 results in an approximate 0.08 magnitude shift to the main sequence turn off location. This means that the mean 0.026 magnitude offset we find in between ACS and HUGS data corresponds to an additional approaximate 0.01 uncertainity in the derived helium mass fraction when comparing between these two datasets.

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=0.9\textwidth]{src/figures/BestFitResults.pdf}
  \caption{Best fit isochrone results for NGC 2808. The best fit population A
  and E models are shown as black lines. The following 50 best fit models are
  presented as grey lines. The solid black line is fit to population A, while
  the dashed black line is fit to population E.}
  \label{fig:BestFitResults}
\end{figure*}

\begin{table*}
  \centering
  \begin{tabular}{c | c c c c c c}
    \hline
    Population & Age & Distance Modulus & Extinction & Y & $\alpha_{ML}$ & $\chi^{2}_{\nu}$\\
    & [Gyr] & & [mag] & & &\\
    \hline
    \hline
    A & 12.996$^{+0.87}_{-0.64}$ & 15.021 & 0.54 & 0.24 & 2.050 & 0.021\\
    E & 13.061$^{+0.86}_{-0.69}$ & 15.007 & 0.537 & 0.39 & 1.600 & 0.033 \\
    \hline
  \end{tabular}
  \caption{Best fit parameters derived from fitting isochrones to the fiducual lines derived from the NCG 2808 photometry. The one sigma uncertainty reported on population age were determined from the 16th and 84th percentiles of the distribution of best fit isochrones ages.}
  \label{tab:BestFitResults}
\end{table*}

@@

{\bf While we make use a purley CMD based approach in this work, other
literature has made use of Chromosome Maps. These consist of implicitly
verticalized pseudo colors. In the chromosome map for NGC 2808 there may be
evidence for more than two populations; however, the process of transforming
magnitude measurements into chromosome space results in dramatically increased
uncertanties for each star. We find a mean fractional uncertantie for
chromosome parameters of $\approx1$ when starting with magnutude
measurements having a mean best-case (i.e. uncertainty assumed to only be due
to Poisson statistics) fractional uncertainty of $\approx 0.0005$. Because of
how \fidanka operates, i.e. resampling a probabilty distribution for each star
in order to idenfify clusters, we are unable to make statisitcally meaningful
statements from the chromosome map}

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.90\textwidth]{src/figures/photometricOffset.pdf}
  \caption{(left) CMD showing the photometric offset between the ACS and HUGS data for NGC 2808. CMDs have been randomly subsampled and colored by point density for clarity. (right) Mean difference between the color of the HUGS and ACS fiducual lines at the same magnitude. Note that the ACS data is systematically bluer than the HUGS data.}
  \label{fig:offset}
\end{figure*}

The oberved photometric offset between ACS and HUGS reductions introduces a
systematic uncertainity when comparing parameters derived from isochrone fits
to ACS data vs those fit to HUGS data. Specifically, this offset introduces a
$\sim 2 Gyr$ uncertainity when comparing ages between ACS and HUGS. Moreover,
for two isochrone of the same age, only seperated by helium mass fraction, a
shift of the main sequence turn off of is also expected. Figure \ref{fig:HeMO}
shows this shift. Note a change in the helium mass fraction of a model by 0.03
results in an approximate 0.08 magnitude shift to the main sequence turn off
location. This means that the mean 0.026 magnitude offset we find in between
ACS and HUGS data corresponds to an additional approaximate 0.01 uncertainity
in the derived helium mass fraction when comparing between these two datasets.

### 2024-03-24 src/sections/intro.tex
Started incorporating ref suggestions into text of the paper

Hot hydrogen burning (proton capture), material transport to the surface, and
material ejection into the intra-cluster media are features of each of these
models and consequently they can all be made to {\it qualitatively} agree with
the observed elemental abundances. However, none of the standard models can
currently account for all specific abundances \citep{Gratton2012}. AGB and FRMS
models are the most promising; however, both models have difficulty reproducing
severe O depletion \citep{Ventura2009,Decressin2007}. Moreover, AGB and FRMS
models require significant mass loss ($\sim 90\%$) between cluster formation
and the current epoch --- implying that a significant fraction of halo stars
formed in GCs \citep{Renzini2008,DErcole2008,Bastian2015}.

In addition to the light-element anti-correlations observed it is also known
that younger populations are significantly enhanced in Helium
\citep{Piotto2007, Piotto2015, Latour2019}. Depending on the cluster, Helium
mass fractions as high as $Y=0.4$ have been inferred \citep[e.g][]{Milone2015}.
However, due to the relatively high and tight temperature range of partial
ionization for He it cannot be observed in globular clusters; consequently, the
evidence for enhanced He in GCs originates from comparison of theoretical
stellar isochrones to the observed color-magnitude-diagrams of globular
clusters. Therefore, a careful handling of chemistry is essential when modeling
with the aim of discriminating between MPs; yet, only a very limited number of
GCs have yet been studied with chemically self-consistent (structure and
atmosphere) isochrones \citep[e.g.][NGC 6752]{Dotter2015}.

NGC 2808 is the prototype globular cluster to host Multiple Populations.
Various studies since 2007 have identified that it may host anywhere from 2-5
stellar populations. These populations have been identified both
spectroscopically \citep[i.e.][]{} and photometrically \citep[i.e.][]{}. Note
that recent work \citep{Valle2022} calls into question the statistical
significance of the detections of more than 2 populations in the spectroscopic
data. Here we present new, chemically self-consistent modeling of the
photometry of the two extreme populations of NGC 2808 identified by
\citet{Milone2015}, populations A and E. We use archival photometry from the
Hubble UV Globular Cluster Survey (HUGS) \citep{Piotto2015, Milone2017} in the
F275W and F814W passbands to charecterize multiple populations in NGC 2808
\citep{Milone2015, Milone2015b}. Additionally, we present a likelihood analysis of the
photometric data of NGC 2808 to determine the number of populations present in
the cluster.

>>>>

Hot hydrogen burning (i.e. proton capture), material transport to the surface, and
material ejection into the intra-cluster media are features of each of these
models and consequently they can all be made to {\it qualitatively} agree with
the observed elemental abundances. However, none of the standard models can
currently account for all specific abundances \citep{Gratton2012}. AGB and FRMS
models are the most promising; however, both models have difficulty reproducing
severe O depletion \citep{Ventura2009,Decressin2007}. Moreover, AGB and FRMS
models require significant mass loss ($\sim 90\%$) between cluster formation
and the current epoch --- implying that a significant fraction of halo stars
formed in GCs \citep{Renzini2008,DErcole2008,Bastian2015}.

In addition to the light-element anti-correlations observed, it is also known
that younger populations are significantly enhanced in Helium
\citep{Piotto2007, Piotto2015, Latour2019}. Depending on the cluster, helium
mass fractions as high as $Y=0.4$ have been inferred \citep[e.g][]{Milone2015}.
However, due to both the relatively high and tight temperature range of partial
ionization for He and the efficiency of gravitational settling in core helium
burning stars, the initial He abundance of globular cluster stars cannot be
observed; consequently, the evidence for enhanced He in GCs originates from
comparison of theoretical stellar isochrones to the observed
color-magnitude-diagrams of globular clusters. Therefore, a careful handling of
chemistry is essential when modeling with the aim of discriminating between
MPs; yet, only a very limited number of GCs have been studied with
chemically self-consistent (structure and atmosphere) isochrones
\citep[e.g.][NGC 6752]{Dotter2015}.

NGC 2808 is the prototype globular cluster to host Multiple Populations.
Various studies since 2007 have identified that it may host anywhere from 2-5
stellar populations. These populations have been identified both
spectroscopically \citep[i.e.][]{Carretta2004, Carretta2006, Carretta2010,
Gratton2011, Carretta2015, Hong2021} and photometrically
\citep[i.e.][]{Piotto2007, Piotto2015, Milone2015, Milone2017, Pasquato2019}.
Note that recent work \citep{Valle2022} calls into question the statistical
significance of the detections of more than 2 populations in the spectroscopic
data. Here we present new, chemically self-consistent modeling of the
photometry of the two extreme populations of NGC 2808 identified by
\citet{Milone2015}, populations A and E. {\bf We do not consider populations B,
C, or D identified in \citet{Milone2015} as the purpose of this work is to
identify if chemically self-consistent modelling results in a statisically
signifigant deviation in the infered helium abundance when compared to non
chemically self-consistent models. Use of the two populations in the NGC 2808
with the highest identified difference between their helium populations is
sufficent for to answer this question.}  We use archival photometry from the
Hubble UV Globular Cluster Survey (HUGS) \citep{Piotto2015, Milone2017} in the
F275W and F814W passbands to characterize multiple populations in NGC 2808
\citep{Milone2015, Milone2015b} (This data is avalible at MAST:
\dataset[10.17909/T9810F]{\doi{10.17909/T9810F}}). Additionally, we present a
likelihood analysis of the photometric data of NGC 2808 to determine the number
of populations present in the cluster.

### 2024-03-24 src/sections/modeling.tex
Started incorporating ref suggestions into text of the paper

We use DSEP to evolve stellar models ranging in mass from 0.3 to 2.0 solar
masses from the fully convective pre-main sequence to the tip of the red giant
branch. Below 0.7 $M_{\odot}$ we evolve a model every 0.03 $M_{\odot}$ and
above 0.7 $M_{\odot}$ we evolve a model every 0.05 $M_{\odot}$. We evolve
models over a grid of mixing length parameters from $\alpha_{MLT} = 1.0$ to
$\alpha_{MLT} = 2.0$ in steps of 0.1. For each mixing length, a grid of models
and isochrones were calculated, with chemical compositions consistent with
Populations A and E (see Table \ref{tab:comp}) and a range of helium abundances
(Y=0.24, 0.27, 0.30, 0.33, 0.36, and 0.39). In total,144 sets of isochrones,
each with a unique composition and mixing length were calculated. Each model is
evolved in DSEP with typical numeric tolerences of one part in $10^{7}$. Each
model is allowed a maximum time step of 50 Myr.

@@

%% Keep a portrait orientation

%% Over-ride the default font size
%% Use Default (12pt)

%% Use \tablewidth{?pt} to over-ride the default table width.
%% If you are unhappy with the default look at the end of the
%% *.log file to see what the default was set at before adjusting
%% this value.

%% This is the title of the table.
\tablecaption{Population Composition}

%% This command over-rides LaTeX's natural table count
%% and replaces it with this number.  LaTeX will increment 
%% all other tables after this table based on this number
\tablenum{1}

%% The \tablehead gives provides the column headers.  It
%% is currently set up so that the column labels are on the
%% top line and the units surrounded by ()s are in the 
%% bottom line.  You may add more header information by writing
%% another line between these lines. For each column that requries
%% extra information be sure to include a \colhead{text} command
%% and remember to end any extra lines with \\ and include the 
%% correct number of &s.
  \tablehead{\colhead{Element} & \colhead{Pop A} & \colhead{Pop E} & \colhead{Element} & \colhead{Pop A} & \colhead{Pop E} 
}

%% All data must appear between the \startdata and \enddata commands
\startdata
Li & -0.08 & --- & In & -1.46 & --- \\
Be & 0.25 & --- & Sn & -0.22 & --- \\
B & 1.57 & --- & Sb & -1.25 & --- \\
C & 6.87 & 5.91 & Te & -0.08 & --- \\
N & 6.42 & 6.69 & I & -0.71 & --- \\
O & 7.87 & 6.91 & Xe & -0.02 & --- \\
F & 3.43 & --- & Cs & -1.18 & --- \\
Ne & 7.12 & 6.7 & Ba & 1.05 & --- \\
Na & 5.11 & 5.7 & La & -0.03 & --- \\
Mg & 6.86 & 6.42 & Ce & 0.45 & --- \\
Al & 5.21 & 6.61 & Pr & -1.54 & --- \\
Si & 6.65 & 6.77 & Nd & 0.29 & --- \\
P & 4.28 & --- & Pm & -99.0 & --- \\
S & 6.31 & 5.89 & Sm & -1.3 & --- \\
Cl & -1.13 & 4.37 & Eu & -0.61 & --- \\
Ar & 5.59 & 5.17 & Gd & -1.19 & --- \\
K & 3.9 & --- & Tb & -1.96 & --- \\
Ca & 5.21 & --- & Dy & -1.16 & --- \\
Sc & 2.02 & --- & Ho & -1.78 & --- \\
Ti & 3.82 & --- & Er & -1.34 & --- \\
V & 2.8 & --- & Tm & -2.16 & --- \\
Cr & 4.51 & --- & Yb & -1.42 & --- \\
Mn & 4.3 & --- & Lu & -2.16 & --- \\
Fe & 6.37 & --- & Hf & -1.41 & --- \\
Co & 3.86 & --- & Ta & -2.38 & --- \\
Ni & 5.09 & --- & W & -1.41 & --- \\
Cu & 3.06 & --- & Re & -2.0 & --- \\
Zn & 2.3 & --- & Os & -0.86 & --- \\
Ga & 0.78 & --- & Ir & -0.88 & --- \\
Ge & 1.39 & --- & Pt & -0.64 & --- \\
As & 0.04 & --- & Au & -1.34 & --- \\
Se & 1.08 & --- & Hg & -1.09 & --- \\
Br & 0.28 & --- & Tl & -1.36 & --- \\
Kr & 0.99 & --- & Pb & -0.51 & --- \\
Rb & 0.26 & --- & Bi & -1.61 & --- \\
Sr & 0.61 & --- & Po & -99.0 & --- \\
Y & 1.08 & --- & At & -99.0 & --- \\
Zr & 1.45 & --- & Rn & -99.0 & --- \\
Nb & -0.8 & --- & Fr & -99.0 & --- \\
Mo & -0.38 & --- & Ra & -99.0 & --- \\
Tc & -99.0 & --- & Ac & -99.0 & --- \\
Ru & -0.51 & --- & Th & -2.2 & --- \\
Rh & -1.35 & --- & Pa & -99.0 & --- \\
Pd & -0.69 & --- & U & -2.8 & --- \\
\enddata

%% Include any \tablenotetext{key}{text}, \tablerefs{ref list},
%% or \tablecomments{text} between the \enddata and 
%% \end{deluxetable} commands

%% General table comment marker
\tablecomments{Relative Metal composition used where a(H) = 12. Where the relative composition is the the same for both populations A and E it is only listed in the population A colum for the sake of visual clarity.}

%% General table references marker
\tablerefs{\citet{Milone2015}}

\end{deluxetable}

>>>>

We use DSEP to evolve stellar models ranging in mass from 0.3 to 2.0 solar
masses from the fully convective pre-main sequence to the tip of the red giant
branch. Below 0.7 $M_{\odot}$ we evolve a model every 0.03 $M_{\odot}$ and
above 0.7 $M_{\odot}$ we evolve a model every 0.05 $M_{\odot}$. We evolve
models over a grid of mixing length parameters from $\alpha_{MLT} = 1.0$ to
$\alpha_{MLT} = 2.0$ in steps of 0.1. For each mixing length, a grid of models
and isochrones were calculated, with chemical compositions consistent with
Populations A and E (see Tables \ref{tab:comp} and \ref{tab:simpleComp}) and a range of helium abundances
(Y=0.24, 0.27, 0.30, 0.33, 0.36, and 0.39). In total,144 sets of isochrones,
each with a unique composition and mixing length were calculated. Each model is
evolved in DSEP with typical numeric tolerences of one part in $10^{7}$. Each
model is allowed a maximum time step of 50 Myr.

@@

\tablecaption{Population Composition}

\tablenum{1}

  \tablehead{\colhead{Element} & \colhead{Pop A} & \colhead{Pop E} & \colhead{Element} & \colhead{Pop A} & \colhead{Pop E} 
}

\startdata
Li & -0.08 & --- & In & -1.46 & --- \\
Be & 0.25 & --- & Sn & -0.22 & --- \\
B & 1.57 & --- & Sb & -1.25 & --- \\
C & 6.87 & 5.91 & Te & -0.08 & --- \\
N & 6.42 & 6.69 & I & -0.71 & --- \\
O & 7.87 & 6.91 & Xe & -0.02 & --- \\
F & 3.43 & --- & Cs & -1.18 & --- \\
Ne & 7.12 & 6.7 & Ba & 1.05 & --- \\
Na & 5.11 & 5.7 & La & -0.03 & --- \\
Mg & 6.86 & 6.42 & Ce & 0.45 & --- \\
Al & 5.21 & 6.61 & Pr & -1.54 & --- \\
Si & 6.65 & 6.77 & Nd & 0.29 & --- \\
P & 4.28 & --- & Pm & -99.0 & --- \\
S & 6.31 & 5.89 & Sm & -1.3 & --- \\
Cl & -1.13 & 4.37 & Eu & -0.61 & --- \\
Ar & 5.59 & 5.17 & Gd & -1.19 & --- \\
K & 3.9 & --- & Tb & -1.96 & --- \\
Ca & 5.21 & --- & Dy & -1.16 & --- \\
Sc & 2.02 & --- & Ho & -1.78 & --- \\
Ti & 3.82 & --- & Er & -1.34 & --- \\
V & 2.8 & --- & Tm & -2.16 & --- \\
Cr & 4.51 & --- & Yb & -1.42 & --- \\
Mn & 4.3 & --- & Lu & -2.16 & --- \\
Fe & 6.37 & --- & Hf & -1.41 & --- \\
Co & 3.86 & --- & Ta & -2.38 & --- \\
Ni & 5.09 & --- & W & -1.41 & --- \\
Cu & 3.06 & --- & Re & -2.0 & --- \\
Zn & 2.3 & --- & Os & -0.86 & --- \\
Ga & 0.78 & --- & Ir & -0.88 & --- \\
Ge & 1.39 & --- & Pt & -0.64 & --- \\
As & 0.04 & --- & Au & -1.34 & --- \\
Se & 1.08 & --- & Hg & -1.09 & --- \\
Br & 0.28 & --- & Tl & -1.36 & --- \\
Kr & 0.99 & --- & Pb & -0.51 & --- \\
Rb & 0.26 & --- & Bi & -1.61 & --- \\
Sr & 0.61 & --- & Po & -99.0 & --- \\
Y & 1.08 & --- & At & -99.0 & --- \\
Zr & 1.45 & --- & Rn & -99.0 & --- \\
Nb & -0.8 & --- & Fr & -99.0 & --- \\
Mo & -0.38 & --- & Ra & -99.0 & --- \\
Tc & -99.0 & --- & Ac & -99.0 & --- \\
Ru & -0.51 & --- & Th & -2.2 & --- \\
Rh & -1.35 & --- & Pa & -99.0 & --- \\
Pd & -0.69 & --- & U & -2.8 & --- \\
\enddata
\tablecomments{Relative Metal composition used where a(H) = 12. Where the relative composition is the the same for both populations A and E it is only listed in the population A colum for the sake of visual clarity.}
\tablerefs{\citet{Milone2015}}
\end{deluxetable}

\begin{deluxetable*}{c|c c c c c c c c c c c}\label{tab:simpleComp}

\tablecaption{Population Abundance Ratios}

\tablenum{2}

  \tablehead{\colhead{Population} & \colhead{[Fe/H]} & \colhead{[$\alpha$/Fe]} & \colhead{[C/Fe]} & \colhead{[N/Fe]} & \colhead{[O/Fe]} & \colhead{[r/Fe]} & \colhead{[s/Fe]} & \colhead{C/O} & \colhead{X} & \colhead{Y} & \colhead{Z} 
}

\startdata
  A & -1.13 & 0.32 & -0.43 & -0.28 & 0.31 & -1.13 & -1.13 & 0.10 & 0.7285 & 0.2700 & 0.00154 \\
  E & -1.13 & -0.11 & -1.39 & -0.02 & -0.66 & -1.13 & -1.13 & 0.10 & 0.7594 & 0.240 & 0.00063
\enddata
\tablecomments{Abundance Ratios for populations A and E in NGC 2808.}
\tablerefs{\citet{Milone2015}}
\end{deluxetable*}
